The Globular Cluster System of the Auriga Simulations

### 2019-03-03 AurigaGCS.tex
Commented some more on MW and M31 GCS observations.

\citet{2019AJ....157...12B} communicate the latest efforts to aggregate all
available data, presented in their CatClu catalog. Amongst 10978 star clusters 
and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC 
candidates. Unfortunately a machine readable version of the catalog is unavailable
at this point in time. Therefore we utilise the H96e10 dataset nonetheless, but
we caution that the Harris catalogue is now believed to be (only) 53-72\% complete.

The relevant data fields that we use from H96e10 are the metallicity [Fe/H], the
Galactic distance components $X$, $Y$, and $Z$ (in kpc)\footnote{In a Sun-centered 
coordinate system where $X$ points toward Galactic center, $Y$ in direction of 
Galactic rotation, and $Z$ toward the North Galactic Pole. We calculate the 
galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2 + Y^2 + Z^2}$, 
assuming $R_\odot=8$~kpc.}, and absolute 
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by 
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$, 
the mean for MW clusters \citep{2005ApJS..161..304M}.

@@

\subsubsection*{Distribution of mass in metallicity-radial bins}
In Fig.~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
metallicity-radial distribution of the MW GCS. In Sec.~\ref{sec:FeHRgc} 
we investigate whether the star formation model implemented in the Auriga 
simulations can produce sufficient total mass in GC candidates in the same bins.

@@

\subsection{Andromeda}
\label{sec:andromeda}
The revised bologna catalogue \citep[][and references therein]{2004A&A...416..917G} 
is the result compiling integrated properties of M31's GCS,

\citet[][, hereafter C11]{2011AJ....141...61C} studied globular clusters in the
Andromeda (M31) galaxy. The relevant fields in this data set are the age, 
metallicities, and absolute visual magnitude.
\todo[inline]{
TODO: paraphrase ``For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$, 
e.g. Strader, Caldwell \& Seth 2011).''
}
For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr, and
the minimum age is 4.8~Gyr.

@@

\todo[inline]{
TODO: paraphrase ``Furthermore, we supplement observational data of globular
clusters in M31 with \citet{2014MNRAS.442.2165H, 2014MNRAS.442.2929V}'', and
parse these data sets.
}

This text sits here just for debug purposes, just for now. We calculate the 
projected and `inferred' galactocentric radius from the observed coordinates.
\begin{align}
    \cos \theta & = \sin \delta_1 \sin \delta_2 +
        \cos \delta_1 \cos \delta_2 \cos \left( \alpha_1 - \alpha_2 \right),
\end{align}
where $(\alpha_1, \delta_1)$ are the right ascension and declination (in degrees,
converted to radians) of the centroid of M31 and $(\alpha_2, \delta_2)$ are the
observed coordinates of the globular cluster. The angle on the sky is converted
to a physical distance in kpc using the small angle approximation, i.e. 
$r_{\text{projected}} = \theta \cdot D_{\text{M31}}$. We adopt the values 
$(\alpha_1, \delta_1) = (0^{\text{h}}42^{\text{m}}44.3^{\text{s}}, 
+41^{\circ}16'9")$ (TODO: reference), and  $D_{\text{M31}} = 778$~kpc 
(TODO: reference).

>>>>

\citet{2019AJ....157...12B} communicate the latest efforts to aggregate the
available data, presented in their CatClu catalog. Amongst 10978 star clusters 
and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC 
candidates. Unfortunately a machine readable version of the catalog is unavailable
at this point in time. Therefore we utilise the H96e10 dataset nonetheless, but
we caution that the Harris catalogue is now believed to be (only) 53-72\% complete.

The relevant data fields that we use from H96e10 are the metallicity [Fe/H], the
Galactic distance components $X$, $Y$, and $Z$ (in kpc)\footnote{In a Sun-centered 
coordinate system: $X$ points toward Galactic center, $Y$ in direction of 
Galactic rotation, and $Z$ toward the North Galactic Pole. We calculate the 
galactocentric radius $R_{\text{GC}}=\sqrt{(X-R_\odot)^2 + Y^2 + Z^2}$, 
assuming the solar radius $R_\odot=8$~kpc.}, and absolute 
magnitude in the V-band $M_V$. We use the latter to calculate mass-estimates by 
assuming $M_{V,\odot}=4.83$ and a mass to light ratio $M/L_V = 1.7$~M/L$_{\odot}$, 
the mean for MW clusters \citep{2005ApJS..161..304M}.

@@

\subsubsection*{Distribution of total GC mass in metallicity-radial bins}
In Fig.~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
metallicity-radial distribution of the MW GCS. In Sec.~\ref{sec:FeHRgc} 
we investigate whether the star formation model implemented in the Auriga 
simulations can produce sufficient total mass in GC candidates in the same bins.

@@

\subsection{Andromeda}
\label{sec:andromeda}
The fifth revision of the revised bologna catalogue (RBC~5, last updated 
August, 2012) is the latest edition of three decades of systematically 
collecting integrated properties of the globular cluster system of the 
Andromeda galaxy \citep[][and references therein]{2004A&A...416..917G}. One
contribution to RBC~5 is the work by \citet[][hereafter C11]{2011AJ....141...61C}. 
C11 delivers a uniform set of spectroscopic observations $316$ out of the 
$339$ GCs in the inner $1^\circ.6 (\sim 21)$~kpc, calibrated using the Milky 
Way GCS.

Globular clusters in the outer halo of M31, up to projected radii 
$R_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological 
Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, see also
\citet{2014MNRAS.442.2929V, 2019MNRAS.484.1756M}. H14 presents the
discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
incorporated in the latest version\footnote{dated 23 Sep 2015; retrieved
from \url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}} 
of the C11 dataset. It seems that the 2015 edition of C11 is the most recent 
aggregated dataset M31's GCS and we will therefore use this troughout the 
remainder of this work.

The relevant fields in the C11 dataset are the age, metallicities, and 
absolute visual magnitude.
\todo[inline]{
TODO: paraphrase ``For M31 GC masses we combine the catalogues of Caldwell et al. (2011, using the 
given masses) and Huxor et al. (2014, again assuming $M/L_V = 1.7$~M/L$_{\odot}$, 
e.g. Strader, Caldwell \& Seth 2011).''
}

For M31 we find an age distribution with a mean value of 10.8$\pm 10.8$~Gyr and a 
dispersion of 2.3~Gyr. Furthermore, 27 GCs have age-estimates below 10~Gyr, and
the minimum age is 4.8~Gyr.

@@

\begin{align}
\end{align}
where $(\alpha_1, \delta_1)$ are the right ascension and declination (in degrees,
We adopt the values 
$(\alpha_0, \delta_0) = (0^{\text{h}}42^{\text{m}}44.3^{\text{s}}, 
+41^{\circ}16'9")$\footnote{See \url{https://ned.ipac.caltech.edu/}} , and  $D_{\text{M31}} = 778$~kpc 
(TODO: reference).
